\documentclass{article}
\usepackage[utf8]{inputenc}
\usepackage{booktabs}
\usepackage{geometry}
\geometry{margin=1in}

\title{Streamlined Aventus-Inspired Fragrance Recipe (1 ml)}
\author{}
\date{}

\begin{document}

\maketitle

\section{Ingredients}

\begin{table}[h]
\centering
\begin{tabular}{lr}
\toprule
\textbf{Ingredient} & \textbf{Amount ($\mu$L)} \\
\midrule
Ethanol (95\%) & 595 \\
Hedione & 230 \\
Iso E Super 10\% (in DPG) & 140 \\
Helvetolide & 140 \\
Bergamot EO & 135 \\
Ambroxan & 100 \\
Patchoulol 23\% (in DPG) & 50 \\
3\% Tonkin Deer Musk Tincture & 30 \\
Lyral & 30 \\
Sweet Orange EO & 20 \\
Pineapple Essence (Robertet) & 20 \\
Petitgrain Absolute 10\% (in DPG) & 15 \\
Coranol & 15 \\
Linalool & 15 \\
Pink Pepper EO & 8 \\
2-Isobutyl Quinoline 10\% (in DPG) & 6 \\
Clary Sage Absolute 23\% (in DPG) & 5 \\
Veramoss (IFF) 23\% & 5 \\
Black Currant Bud Absolute 10\% (in IPM) & 3 \\
Damascone Alpha 10\% (in DPG) & 3 \\
Neroli Oil & 2 \\
Birch Tar 1\% & 2 \\
\bottomrule
\end{tabular}
\end{table}

\section{Preparation Instructions}

\begin{enumerate}
    \item \textbf{Prepare Dilutions} (if not already prepared):
    \begin{itemize}
        \item Patchoulol 23\%: 230 microliters Patchoulol + 770 microliters DPG
        \item Iso E Super 10\%: 1 g Iso E Super + 9 g DPG
        \item Petitgrain Absolute 10\%: 100 microliters Petitgrain Absolute + 900 microliters DPG
        \item Clary Sage Absolute 23\%: 230 microliters Clary Sage Absolute + 770 microliters DPG
        \item 2-Isobutyl Quinoline 10\%: 100 microliters 2-IBQ + 900 microliters DPG
        \item Damascone Alpha 10\%: 100 microliters Damascone Alpha + 900 microliters DPG
        \item Black Currant Bud Absolute 10\%: 100 microliters absolute + 900 microliters IPM
    \end{itemize}
    
    \item Add 595 microliters Ethanol (95\%) to a 1 ml amber glass vial.
    
    \item Add ingredients in the following order using separate micropipette tips:
    \begin{itemize}
        \item \textbf{Base Notes}: Patchoulol 23\%, 3\% Tonkin Deer Musk Tincture, Iso E Super 10\%, Helvetolide, Ambroxan, Veramoss 23\%
        \item \textbf{Heart Notes}: 2-Isobutyl Quinoline 10\%, Black Currant Bud Absolute 10\%, Damascone Alpha 10\%, Clary Sage Absolute 23\%, Birch Tar 1\%
        \item \textbf{Florals \& Spices}: Pink Pepper EO, Petitgrain Absolute 10\%, Linalool, Coranol, Lyral, Neroli Oil
        \item \textbf{Citrus \& Fruits}: Sweet Orange EO, Bergamot EO, Pineapple Essence
        \item \textbf{Finally}: Hedione
    \end{itemize}
    
    \item Seal vial, roll gently for 1--2 minutes to blend.
    
    \item Rest for 48--72 hours in a cool, dark place.
    
    \item Test on skin, adjusting if needed.
\end{enumerate}

\section{Expected Scent Profile}

\begin{itemize}
    \item \textbf{Top (5--30 min)}: Bright pineapple-citrus opening with bergamot and sweet orange creating a fresh, sparkling introduction. Pink pepper adds warmth and subtle spice.
    
    \item \textbf{Heart (30 min -- 3 hr)}: Hedione provides the main floral-citrus radiance. Rose-birch tar combination with black currant tartness. Petitgrain and clary sage add green-herbal complexity. Clean and focused without competing florals.
    
    \item \textbf{Base (3--8+ hr)}: Clean chypre foundation from patchoulol and veramoss. Sophisticated musky backbone from deer musk, Helvetolide, and Ambroxan. Iso E Super provides radiance and longevity throughout the wear.
\end{itemize}

\textbf{Performance}: 6--8 hours, excellent projection and sillage. Clean, focused Aventus character.

\textbf{Key Features}: Streamlined formula focusing on essential Aventus DNA. Hedione-dominant heart with clean synthetic backbone. Eliminates competing notes for better clarity and performance.

\textbf{Changes from Original}: Removed redundant florals, multiple patchouli sources, heavy resins, and competing musks. Increased bergamot to compensate for missing linalyl acetate. Maintained deer musk as quality musky anchor.

\end{document}