\documentclass{article}
\usepackage[utf8]{inputenc}
\usepackage{booktabs}
\usepackage{geometry}
\geometry{margin=1in}

\title{Aventus-Inspired Fragrance Recipe (1 ml)}
\author{}
\date{}

\begin{document}

\maketitle

\section{Ingredients}

\begin{table}[h]
\centering
\begin{tabular}{lr}
\toprule
\textbf{Ingredient} & \textbf{Amount ($\mu$L)} \\
\midrule
Ethanol (95\%) & 400 \\
Bergamot EO & 100 \\
Patchoulol 10\% (in DPG) & 50 \\
Sweet Orange EO & 20 \\
Petitgrain Absolute & 15 \\
Pink Pepper EO & 8 \\
Clary Sage Absolute & 5 \\
Neroli EO & 2 \\
Black Currant Bud Absolute 10\% (in IPM) & 6 \\
Birch Tar 1\% (in DPG) & 2 \\
Paradisamide 10\% (in DPG) & 235 \\
Star Anise EO & 6 \\
Pineapple Essence (Natural) & 5 \\
Iso E Super 10\% (in DPG) & 140 \\
Helvetolide & 140 \\
3\% Tonkin Deer Musk Tincture & 50 \\
Galaxolide & 20 \\
Linalyl Acetate & 30 \\
Coranol & 15 \\
Lyral & 30 \\
Linalool & 15 \\
Veramoss 10\% (in DPG) & 5 \\
Isobutyl Quinoline 10\% & 6 \\
Damascone Alpha 10\% & 3 \\
\bottomrule
\end{tabular}
\end{table}

\section{Preparation Instructions}

\begin{enumerate}
    \item \textbf{Prepare Dilutions}:
    \begin{itemize}
        \item Veramoss 10\%: 1 g Veramoss + 9 g DPG, warm to 40--50°C if needed.
        \item Patchoulol 10\%: 1 g Patchoulol + 9 g DPG, warm if needed.
        \item Birch Tar 1\%: 10 microliters Birch Tar + 990 microliters DPG.
        \item Black Currant Bud Absolute 50\% (optional): 500 microliters 10\% + 500 microliters undiluted (or use 10\%).
        \item Paradisamide 10\%: 100 microliters Paradisamide + 900 microliters DPG.
    \end{itemize}
    
    \item Add 400 microliters ethanol to a 1 ml amber glass vial.
    
    \item Add ingredients in order using separate micropipette tips: Patchoulol 10\%, Deer Musk Tincture, Iso E Super 10\%, Helvetolide, Galaxolide, Veramoss 10\%, Isobutyl Quinoline 10\%, Birch Tar 1\%, Black Currant 10\%, Damascone Alpha 10\%, Clary Sage, Neroli, Pink Pepper, Petitgrain, Linalool, Coranol, Linalyl Acetate, Lyral, Sweet Orange, Star Anise, Bergamot, Pineapple Essence, Paradisamide 10\%.
    
    \item Seal vial, roll gently for 1--2 minutes to blend.
    
    \item Rest for 48 hours in a cool, dark place.
    
    \item Test on skin, adjusting deer musk (30--60 microliters), Paradisamide (200--260 microliters), or Veramoss (5--10 microliters) if needed.
\end{enumerate}

\section{Expected Scent Profile}

\begin{itemize}
    \item \textbf{Top (5--30 min)}: Pineapple, bergamot, orange, star anise, and pink pepper for a fruity-citrus-anisic burst.
    
    \item \textbf{Heart (30 min -- 3 hr)}: Neroli, petitgrain, clary sage, black currant, and florals (Lyral, Linalyl Acetate, Coranol) for a juicy, spicy core.
    
    \item \textbf{Base (3--8+ hr)}: Patchoulol, Helvetolide, deer musk, Galaxolide, Veramoss, and birch tar for a musky-woody-chypre drydown.
\end{itemize}

\textbf{Performance}: 5--7 hours, moderate projection, cologne-like crispness.

\end{document}