\documentclass{article}
\usepackage[utf8]{inputenc}
\usepackage{booktabs}
\usepackage{geometry}
\geometry{margin=1in}

\title{Integrated Aventus-Inspired Formula with Suralette Elements (1 ml)}
\author{}
\date{}

\begin{document}

\maketitle

\section{Complete Formula Ingredients}

\begin{table}[h]
\centering
\begin{tabular}{lr}
\toprule
\textbf{Ingredient} & \textbf{Amount ($\mu$L)} \\
\midrule
Ethanol (95\%) & 507 \\
Hedione & 230 \\
Iso E Super 10\% (in DPG) & 140 \\
Helvetolide & 140 \\
Bergamot EO & 100 \\
Ambroxan & 100 \\
Patchouli EO & 40 \\
Melissa EO & 30 \\
3\% Tonkin Deer Musk Tincture & 30 \\
Galaxolide & 30 \\
Lyral & 30 \\
Linalyl Acetate & 20 \\
Sweet Orange EO & 20 \\
Pineapple Essence (Robertet) & 20 \\
Petitgrain Absolute 50\% (in DPG) & 30 \\
Coranol & 15 \\
Linalool & 15 \\
Sandalwood Absolute 20\% (in DPG) & 15 \\
Patchoulol 23\% (in DPG) & 10 \\
Mimosa Absolute 50\% (in DPG/Ethanol) & 10 \\
Galbanum Absolute 10\% (in DPG) & 10 \\
Pink Pepper EO & 8 \\
Star Anise EO & 8 \\
2-Isobutyl Quinoline 10\% (in DPG) & 6 \\
Clary Sage Absolute 23\% (in DPG) & 5 \\
Veramoss (IFF) 23\% & 5 \\
Birch Tar 1\% & 5 \\
C-12 MNA (Aldehyde) & 4 \\
Black Currant Bud Absolute 10\% (in IPM) & 3 \\
Damascone Alpha 10\% (in DPG) & 3 \\
Neroli Oil & 2 \\
Methyl Benzoate & 2 \\
\bottomrule
\end{tabular}
\end{table}

\section{Preparation Instructions}

\begin{enumerate}
    \item Add 507 microliters Ethanol (95\%) to a 1ml amber glass vial.
    
    \item Add ingredients in the following order using separate micropipette tips:
    \begin{itemize}
        \item \textbf{Woody Base}: Patchouli EO, Patchoulol 23\%, Sandalwood Absolute 20\%
        \item \textbf{Musk Foundation}: Deer Musk Tincture, Galaxolide, Helvetolide, Ambroxan
        \item \textbf{Radiance \& Woods}: Iso E Super 10\%, Veramoss 23\%
        \item \textbf{Smoky Heart}: 2-Isobutyl Quinoline 10\%, Birch Tar 1\%
        \item \textbf{Fruity Heart}: Black Currant Absolute 10\%, Damascone Alpha 10\%
        \item \textbf{Herbal-Anisic Complex}: Melissa EO, Star Anise, Mimosa Absolute 50\%, Galbanum Absolute 10\%, Methyl Benzoate
        \item \textbf{Floral Bridge}: Clary Sage Absolute 23\%, Petitgrain Absolute 50\%
        \item \textbf{Spice \& Florals}: Pink Pepper, Linalool, Coranol, Lyral, Neroli
        \item \textbf{Citrus \& Aldehydes}: Bergamot, Sweet Orange, Linalyl Acetate, C-12 MNA
        \item \textbf{Fruit}: Pineapple Essence
        \item \textbf{Finally}: Hedione
    \end{itemize}
    
    \item Seal vial, roll gently for 1--2 minutes to blend.
    
    \item Rest for 48--72 hours in a cool, dark place before testing.
\end{enumerate}

\section{Scent Profile}

\begin{itemize}
    \item \textbf{Opening (0-30 min)}: Bright citrus sparkle from bergamot and C-12 MNA aldehydic lift. Pineapple provides tropical freshness while melissa adds herbal-citrus complexity.
    
    \item \textbf{Heart (30 min - 3 hr)}: Hedione dominates with radiant floral-citrus character. Integrated herbal complexity from melissa, star anise, and mimosa creates sophisticated anisic-green depth. Smoky birch tar and rosy damascone provide Aventus DNA. Sandalwood adds creamy woody warmth.
    
    \item \textbf{Base (3-8+ hr)}: Authentic patchouli foundation (EO + patchoulol) with galaxolide softness. Deer musk and helvetolide provide animalic-clean musk backbone. Iso E Super ensures lasting radiance.
\end{itemize}

\section{Key Features}

\begin{itemize}
    \item \textbf{Integrated Herbal Complexity}: Melissa, star anise, mimosa, and galbanum provide sophisticated green-anisic character throughout the wear
    \item \textbf{Authentic Patchouli}: 40$\mu$L EO + 10$\mu$L patchoulol for full earthy-woody spectrum
    \item \textbf{Enhanced Citrus}: Linalyl acetate + C-12 MNA + bergamot for sparkling projection
    \item \textbf{Balanced Musk Foundation}: Galaxolide softness + deer musk richness + helvetolide performance
    \item \textbf{Unified Composition}: All elements work together rather than separate accords
\end{itemize}

\textbf{Performance}: 7--9 hours with excellent projection and sophisticated complexity. The integrated herbal elements add depth without competing with the core Aventus DNA.

\end{document}