\documentclass{article}
\usepackage{geometry}
\usepackage{xcolor}
\usepackage{titlesec}
\usepackage{enumitem}
\usepackage{fancyhdr}
\usepackage{booktabs}
\usepackage{array}

% Define cola-inspired colors
\definecolor{colaRed}{RGB}{201, 37, 44}     % Deep red like Coca-Cola logo
\definecolor{colaBrown}{RGB}{58, 29, 20}    % Dark brown like cola liquid
\definecolor{colaCream}{RGB}{253, 246, 227} % Light cream for background
\definecolor{colaDark}{RGB}{45, 12, 7}      % Deep dark brown
\definecolor{violetPurple}{RGB}{138, 93, 150} % Violet flower color

% Page setup
\geometry{margin=1in}

% Header and footer setup
\pagestyle{fancy}
\fancyhf{}
\renewcommand{\headrulewidth}{0.4pt}
\renewcommand{\footrulewidth}{0.4pt}
\fancyhead[C]{\textcolor{violetPurple}{\textbf{Artisan Natural Fragrance Recipe (Coca-Cola Forest)}}}
\fancyfoot[C]{\textcolor{colaBrown}{\thepage}}

% Title format
\titleformat{\section}
  {\normalfont\Large\bfseries\color{colaRed}}
  {\thesection}{1em}{}

% Document begins
\begin{document}

\begin{center}
\textcolor{violetPurple}{\LARGE\textbf{Violet Cola Flower (Coca-Cola Forest)}}\\[0.5cm]
\textcolor{colaBrown}{\large\textit{A natural fragrance evoking Coca-Cola in a forest near a bonfire, vibrant for summer/spring}}\\[0.5cm]
\end{center}

\section*{Naturals-Only 1ml Fragrance Recipe}

\begin{center}
\begin{tabular}{p{6.5cm}r}
\toprule
\textcolor{colaRed}{\textbf{Ingredient}} & \textcolor{colaRed}{\textbf{Amount}} \\
\midrule
\multicolumn{2}{l}{\textcolor{violetPurple}{\textbf{Order of Addition (Bottom to Top):}}} \\
\midrule
IPM (Carrier) & 740 microliters \\
3\% Deer Musk Tincture & 30 microliters \\
10\% Boronia Absolute (in IPM) & 35 microliters \\
$\sim$10\% Black Currant Bud Absolute (in IPM) & 6 microliters \\
10\% Vanilla Absolute (in IPM) & 10 microliters \\
10\% Violet Leaf Absolute (in IPM) & 20 microliters \\
10\% Frankincense Absolute (in IPM) & 40 microliters \\
10\% Myrrh Absolute (in IPM) & 15 microliters \\
Nutmeg Absolute & 5 microliters \\
Neroli EO & 15 microliters \\
Pink Pepper EO (undiluted) & 12 microliters \\
Ceylon Cinnamon EO & 7 microliters \\
Lime EO & 30 microliters \\
Lemon EO & 25 microliters \\
Bergamot EO & 65 microliters \\
\bottomrule
\end{tabular}
\end{center}

\vspace{0.5cm}

\section*{Concentration Analysis}
\begin{itemize}[leftmargin=*]
  \item \textcolor{colaRed}{\textbf{Citrus Notes (12\%):}}
  \begin{itemize}
    \item Bergamot Essential Oil: 65 microliters (6.5\%)
    \item Lime Essential Oil: 30 microliters (3\%)
    \item Lemon Essential Oil: 25 microliters (2.5\%)
  \end{itemize}
  
  \item \textcolor{colaRed}{\textbf{Spice Elements (2.4\%):}}
  \begin{itemize}
    \item Ceylon Cinnamon Essential Oil: 7 microliters (0.7\%)
    \item Pink Pepper Essential Oil: 12 microliters (1.2\%)
    \item Nutmeg Absolute: 5 microliters (0.5\%)
  \end{itemize}
  
  \item \textcolor{violetPurple}{\textbf{Floral \& Incense Notes (2.4\%):}}
  \begin{itemize}
    \item 10\% Violet Leaf Absolute: 20 microliters (0.2\% final)
    \item 10\% Boronia Absolute: 35 microliters (0.35\% final)
    \item 10\% Frankincense Absolute: 40 microliters (0.4\% final)
    \item 10\% Myrrh Absolute: 15 microliters (0.15\% final)
    \item Neroli Essential Oil: 15 microliters (1.5\% final)
  \end{itemize}
  
  \item \textcolor{colaBrown}{\textbf{Fruit \& Base Notes (0.26\%):}}
  \begin{itemize}
    \item $\sim$10\% Black Currant Bud Absolute: 6 microliters ($\sim$0.07\% final)
    \item 10\% Vanilla Absolute: 10 microliters (0.1\% final)
    \item 3\% Deer Musk Tincture: 30 microliters (0.09\% final)
  \end{itemize}
  
  \item \textcolor{colaBrown}{\textbf{Carrier:}}
  \begin{itemize}
    \item Isopropyl Myristate (IPM): 740 microliters (74\%)
  \end{itemize}
\end{itemize}

\section*{Expected Scent Profile}

\paragraph{\textcolor{colaRed}{\textbf{Top Notes (5-30 minutes):}}}
Vibrant bergamot, lime, and lemon with pink pepper’s fruity-spicy kick and violet leaf’s green floralcy, evoking Coca-Cola’s fizzy sparkle in a summer forest.

\paragraph{\textcolor{colaBrown}{\textbf{Heart Notes (30 min - 4 hours):}}}
Boronia’s tea-like, fruity-floral blooms with neroli’s springtime lift and frankincense’s bonfire warmth. Black currant adds Coca-Cola tang, with nutmeg and cinnamon for forest spice.

\paragraph{\textcolor{colaDark}{\textbf{Base Notes (4-10+ hours):}}}
Frankincense and myrrh’s smoky incense with vanilla’s subtle Coca-Cola sweetness and deer musk’s ember-like warmth, grounding the forest scene.

\paragraph{\textcolor{violetPurple}{\textbf{Overall Performance:}}}
8-10 hours with strong projection, effervescent and evocative, capturing Coca-Cola in a summer/spring forest near a bonfire, primed for synthetics.

\section*{Preparation Instructions}
\begin{enumerate}
  \item Prepare resin dilutions: Combine 100 microliters frankincense or myrrh resin powder with 900 microliters IPM per 1ml vial. Shake, rest 24-48 hours, warm to 40-50°C if needed.
  \item Begin with 740 microliters IPM in a 1ml vial.
  \item Add ingredients in order, using separate micropipette tips:
  \begin{itemize}
    \item Tip 1: IPM
    \item Tip 2: 3\% Deer Musk Tincture
    \item Tip 3: 10\% Boronia Absolute
    \item Tip 4: $\sim$10\% Black Currant Bud Absolute
    \item Tip 5: 10\% Vanilla Absolute
    \item Tip 6: 10\% Violet Leaf Absolute
    \item Tip 7: 10\% Frankincense Absolute
    \item Tip 8: 10\% Myrrh Absolute
    \item Tip 9: Nutmeg Absolute
    \item Tip 10: Neroli EO
    \item Tip 11: Pink Pepper EO
    \item Tip 12: Ceylon Cinnamon EO
    \item Tip 13: Lime EO
    \item Tip 14: Lemon EO
    \item Tip 15: Bergamot EO
  \end{itemize}
  \item Seal vial, roll gently to blend without air bubbles.
  \item Rest 48-72 hours in a cool, dark place.
  \item Test on skin, noting boronia’s blooms, violet-incense bonfire, and Coca-Cola fizz.
\end{enumerate}

\section*{Notes for Future Batches}
\begin{itemize}
  \item If boronia is too floral, reduce to 30 microliters; if muted, increase to 40 microliters.
  \item If incense is too smoky, reduce frankincense to 35 microliters or myrrh to 10 microliters.
  \item If black currant is too tangy, reduce to 5 microliters; if faint, increase to 7 microliters.
  \item Warm viscous absolutes to 40-50°C for handling.
  \item Remake 10\% dilutions with DPG when available.
  \item Store resins and black currant absolute (approximately 1.9g) in fridge.
  \item Test synthetics (Iso E Super at 50 microliters, hedione at 50 microliters, calone at 2 microliters, ambroxan at 15 microliters) in a 1ml batch.
\end{itemize}

\vspace{1cm}
\begin{center}
\textcolor{violetPurple}{\rule{0.8\textwidth}{0.4pt}}
\end{center}

\begin{center}
\textit{\textcolor{colaDark}{A vibrant, unisex fragrance capturing Coca-Cola’s fizz in a summer/spring forest near a smoky bonfire, with blooming boronia and resinous warmth.}}
\end{center}

\end{document}