\documentclass{article}
\usepackage[utf8]{inputenc}
\usepackage{booktabs}
\usepackage{geometry}
\geometry{margin=1in}

\title{Clean-Smoky Aventus Formula (750$\mu$L Scale)}
\author{}
\date{}

\begin{document}

\maketitle

\section{Complete Formula Ingredients}

\begin{table}[h]
\centering
\begin{tabular}{lr}
\toprule
\textbf{Ingredient} & \textbf{Amount ($\mu$L)} \\
\midrule
Ethanol (95\%) & 156 \\
Hedione & 77 \\
Iso E Super & 47 \\
Helvetolide & 47 \\
Bergamot EO & 33 \\
Ambroxan 10\% (in DPG) & 330 \\
Galaxolide 27\% (in DPG) & 29 \\
Patchouli EO & 13 \\
Petitgrain Absolute 50\% (in DPG) & 10 \\
Birch Tar 1\% & 7 \\
Linalyl Acetate & 7 \\
Lyral & 7 \\
Violet Leaf Absolute 10\% (in DPG) & 5 \\
Black Currant Bud Absolute 10\% (in IPM) & 5 \\
Coranol & 5 \\
Linalool & 5 \\
Clary Sage Absolute 23\% (in DPG) & 4 \\
Patchoulol 23\% (in DPG) & 3 \\
Pink Pepper EO & 3 \\
Boronia Absolute 10\% (in DPG) & 3 \\
2-Isobutyl Quinoline 10\% (in DPG) & 2 \\
Veramoss (IFF) 23\% & 2 \\
Neroli Oil & 1 \\
Damascone Alpha 10\% (in DPG) & 1 \\
\bottomrule
\end{tabular}
\end{table}

\section{Preparation Instructions}

\begin{enumerate}
    \item Add 95 microliters Ethanol (95\%) to a 1ml amber glass vial.
    
    \item Add ingredients in the following order using separate micropipette tips:
    \begin{itemize}
        \item \textbf{Base \& Musk Foundation}: Hedione, Helvetolide, Galaxolide 27\%, Ambroxan 10\%, Iso E Super
        \item \textbf{Smoky Core}: Birch Tar, 2-Isobutyl Quinoline
        \item \textbf{Green-Resinous Complex}: Violet Leaf Absolute (18$\mu$L), Petitgrain Absolute, Clary Sage Absolute, Cypress Absolute, Galbanum, Cistus Absolute
        \item \textbf{Floral \& Fruit}: Boronia Absolute, Neroli, Lyral, Black Currant Bud Absolute, Pineapple Essence (2.2$\mu$L)
        \item \textbf{Woody-Earthy Foundation}: Patchouli EO, Patchoulol, Pink Pepper
        \item \textbf{Citrus Top}: Bergamot, Linalyl Acetate, Linalool, Coranol
        \item \textbf{Final Touches}: Veramoss, Damascone Alpha
    \end{itemize}
    
    \item Seal vial, roll gently for 1--2 minutes to blend.
    
    \item Rest for 48--72 hours in a cool, dark place before testing.
\end{enumerate}

\section{Scent Profile}

\begin{itemize}
    \item \textbf{Opening (0-30 min)}: Sophisticated bergamot sparkle with substantial violet leaf greenness (18$\mu$L), clean petitgrain bitterness, and precise pineapple essence (2.2$\mu$L). Black currant adds green-fruity tartness while galbanum provides sharp green intensity.
    
    \item \textbf{Heart (30 min - 3 hr)}: Galaxolide's clean powder foundation meets birch tar's refined smoke with cypress adding resinous depth. Hedione provides radiant floral-citrus lift while boronia adds honeyed-floral sophistication. Massive ambroxan foundation provides ultimate ozonic smoothness. Enhanced patchouli complexity from 13$\mu$L EO + 12$\mu$L patchoulol 27\%. Cistus adds leathery-animalic depth.
    
    \item \textbf{Base (3-8+ hr)}: Galaxolide and helvetolide create lasting clean-powdery musk foundation. Patchouli provides earthy depth while birch tar maintains distinctive smoky signature. Iso E Super ensures transparent woody radiance.
\end{itemize}

\section{Key Features}

\begin{itemize}
    \item \textbf{Perfect Ambrettolide Substitute}: 87$\mu$L galaxolide 27\% = 23.5$\mu$L actual (matches 20$\mu$L ambrettolide)
    \item \textbf{Proper Ambroxan Foundation}: 330$\mu$L at 10\% = 33$\mu$L actual (10x more than previous attempts)
    \item \textbf{Galaxolide-Patchouli-Birch Tar Trinity}: Clean powder, earthy musk, and sophisticated smoke
    \item \textbf{Black Currant Accent}: Subtle green-fruity tartness that bridges clean and smoky elements
    \item \textbf{Concentrated Formula}: 750$\mu$L total for testing with proper ambroxan ratios
    \item \textbf{Scalable Design}: Can be multiplied by 3 for full 1ml batch once perfected
\end{itemize}

\textbf{Performance}: Expected 6--8 hours with good projection. Concentrated format allows for precise testing and adjustment before scaling up.

\textbf{Scaling Note}: To make full 1ml batch, multiply all amounts by 1.33 (1000รท750).

\end{document}