\documentclass{article}
\usepackage{geometry}
\usepackage{xcolor}
\usepackage{titlesec}
\usepackage{enumitem}
\usepackage{fancyhdr}
\usepackage{booktabs}
\usepackage{array}

% Define cola-inspired colors
\definecolor{colaRed}{RGB}{201, 37, 44}     % Deep red like Coca-Cola logo
\definecolor{colaBrown}{RGB}{58, 29, 20}    % Dark brown like cola liquid
\definecolor{colaCream}{RGB}{253, 246, 227} % Light cream background
\definecolor{colaDark}{RGB}{45, 12, 7}      % Deep dark brown
\definecolor{violetPurple}{RGB}{138, 93, 150} % Violet flower color

% Page setup
\geometry{margin=1in}

% Header and footer setup
\pagestyle{fancy}
\fancyhf{}
\renewcommand{\headrulewidth}{0.4pt}
\renewcommand{\footrulewidth}{0.4pt}
\fancyhead[C]{\textcolor{violetPurple}{\textbf{Peach Tea Beard Balm}}}
\fancyfoot[C]{\textcolor{colaBrown}{\thepage}}

% Title format
\titleformat{\section}
  {\normalfont\Large\bfseries\color{colaRed}}
  {\thesection}{1em}{}

% Document begins
\begin{document}

\begin{center}
\textcolor{violetPurple}{\LARGE\textbf{Peach Tea Beard Balm}}\\[0.5cm]
\textcolor{colaBrown}{\large\textit{A natural, refreshing balm with tart fruity-floral notes, green crispness, and subtle resinous depth}}\\[0.5cm]
\end{center}

\section*{Naturals-Only 30ml Beard Balm Recipe}

\begin{center}
\begin{tabular}{p{6.5cm}r}
\toprule
\textcolor{colaRed}{\textbf{Ingredient}} & \textcolor{colaRed}{\textbf{Amount}} \\
\midrule
\multicolumn{2}{l}{\textcolor{violetPurple}{\textbf{Base Composition:}}} \\
\midrule
Carnauba Wax & 4.5 grams (15\%) \\
Kokum Butter & 9 grams (30\%) \\
Squalane & 15.7 grams (52.33\%) \\
Scent Blend (Oils/Absolutes + Diluent) & 0.8 ml (2.67\%) \\
\midrule
\multicolumn{2}{l}{\textcolor{violetPurple}{\textbf{Scent Blend Composition (800 microliters):}}} \\
\midrule
3\% Deer Musk Tincture & 30 microliters \\
10\% Black Currant Bud Absolute (in IPM) & 120 microliters \\
10\% Violet Leaf Absolute (in IPM) & 140 microliters \\
10\% Boronia Absolute (in IPM) & 80 microliters \\
Orange Blossom Absolute & 80 microliters \\
Neroli EO & 30 microliters \\
Pink Pepper EO (undiluted) & 30 microliters \\
Coriander EO & 50 microliters \\
Lemon EO & 50 microliters \\
Frankincense Frereana EO & 20 microliters \\
Dipropylene Glycol (DPG) or Isopropyl Myristate (IPM) & 300 microliters \\
\bottomrule
\end{tabular}
\end{center}

\vspace{0.5cm}

\section*{Concentration Analysis}
\begin{itemize}[leftmargin=*]
  \item \textcolor{colaRed}{\textbf{Floral-Fruity Notes (0.381\% in balm):}}
  \begin{itemize}
    \item 10\% Black Currant Bud Absolute: 120 microliters (0.04\% final)
    \item 10\% Violet Leaf Absolute: 140 microliters (0.047\% final)
    \item 10\% Boronia Absolute: 80 microliters (0.027\% final)
    \item Orange Blossom Absolute: 80 microliters (0.267\% final)
  \end{itemize}
  
  \item \textcolor{colaRed}{\textbf{Floral Support (0.1\% in balm):}}
  \begin{itemize}
    \item Neroli Essential Oil: 30 microliters (0.1\% final)
  \end{itemize}
  
  \item \textcolor{colaRed}{\textbf{Spice Notes (0.267\% in balm):}}
  \begin{itemize}
    \item Pink Pepper Essential Oil: 30 microliters (0.1\% final)
    \item Coriander Essential Oil: 50 microliters (0.167\% final)
  \end{itemize}
  
  \item \textcolor{violetPurple}{\textbf{Citrus Note (0.167\% in balm):}}
  \begin{itemize}
    \item Lemon Essential Oil: 50 microliters (0.167\% final)
  \end{itemize}
  
  \item \textcolor{violetPurple}{\textbf{Resinous-Musk Notes (0.07\% in balm):}}
  \begin{itemize}
    \item Frankincense Frereana Essential Oil: 20 microliters (0.067\% final)
    \item 3\% Deer Musk Tincture: 30 microliters (0.003\% final)
  \end{itemize}
  
  \item \textcolor{colaBrown}{\textbf{Carrier (Diluent in Scent Blend):}}
  \begin{itemize}
    \item Dipropylene Glycol (DPG) or Isopropyl Myristate (IPM): 300 microliters
  \end{itemize}
\end{itemize}

\section*{Expected Scent Profile}

\paragraph{\textcolor{colaRed}{\textbf{On Application:}}}
A vibrant burst of black currant’s tangy, sulfurous fruitiness, violet leaf’s crisp, cucumber-green fizz, and lemon’s bright, tart sparkle, with pink pepper’s fruity-spicy zing, evokes a cool Kyushu tea field under a sunny sky, humble yet lively like a morning breeze.

\paragraph{\textcolor{colaBrown}{\textbf{Mid Wear (30 min - 2 hours):}}}
Boronia’s ionone-rich, tea-like floralcy blooms alongside orange blossom’s lush, flowery radiance, with neroli’s honeyed glow and coriander’s bold, citrusy-spicy spark. The heart is refreshing, with tart fruit and green florals painting a tea field alive with blooms, its Rush-like vibrancy slyly complex beneath a simple facade.

\paragraph{\textcolor{colaDark}{\textbf{Dry Down (2-6+ hours):}}}
Frankincense’s subtle, resinous warmth and deer musk’s musky depth settle in, with traces of boronia and violet leaf, offering a dry, chypre-like finish. The dry down is understated, like a Scottish meadow at dusk, yet evocative, grounding the tea field’s crispness with intimate elegance.

\paragraph{\textcolor{violetPurple}{\textbf{Overall Performance:}}}
Peach Tea Beard Balm wears for 4-6 hours with subtle projection, a natural, artisanal blend that’s crisp and refreshing, with tart black currant, green violet leaf, blooming boronia-orange blossom, zesty lemon, and a resinous frankincense base. It contrasts Peach Tea’s spicy chypre with summery vibrancy, perfect for a half-Japanese, half-Scottish teacher’s rugged, bearded charm.

\section*{Preparation Instructions}
\begin{enumerate}
  \item \textbf{Pre-Blend Scent Compounds:}
  \begin{itemize}
    \item In a 1-2ml glass vial, combine the following in order, using separate micropipette tips:
    \begin{itemize}
      \item 3\% Deer Musk Tincture: 30 microliters
      \item 10\% Black Currant Bud Absolute (in IPM): 120 microliters
      \item 10\% Violet Leaf Absolute (in IPM): 140 microliters
      \item 10\% Boronia Absolute (in IPM): 80 microliters
      \item Orange Blossom Absolute: 80 microliters
      \item Neroli Essential Oil: 30 microliters
      \item Pink Pepper Essential Oil: 30 microliters
      \item Coriander Essential Oil: 50 microliters
      \item Lemon Essential Oil: 50 microliters
      \item Frankincense Frereana Essential Oil: 20 microliters
    \end{itemize}
    \item Add 300 microliters of Dipropylene Glycol (DPG, preferred) or Isopropyl Myristate (IPM, fallback).
    \item Seal vial and roll gently for 1-2 minutes to blend, warming to 40-50°C if absolutes (black currant, violet leaf, boronia, orange blossom) are viscous.
    \item Rest for 1-2 hours (or up to 24 hours for optimal melding).
    \item Test on wrist, noting black currant’s tartness, violet leaf’s crispness, orange blossom’s floralcy, lemon’s zest, and frankincense’s depth. Adjust if needed (e.g., add 10 microliters coriander for spice).
  \end{itemize}
  \item \textbf{Melt Base:} In a double boiler, melt carnauba wax (4.5 grams) and kokum butter (9 grams) over low heat until liquid, stirring gently.
  \item \textbf{Add Squalane:} Remove from heat, add squalane (15.7 grams), and stir until blended.
  \item \textbf{Cool Slightly:} Cool to approximately 40-50°C to preserve the scent blend.
  \item \textbf{Add Scent Blend:} Add the pre-blended scent mixture (800 microliters) to the base, stirring gently to integrate.
  \item \textbf{Pour and Set:} Pour into a 30ml tin or jar while warm, cool at room temperature for 4-6 hours until solid, and seal tightly.
  \item \textbf{Test Application:} Apply a small amount to your beard, noting the balance of tartness, floralcy, crispness, and resinous depth. Adjust in future batches if needed.
\end{enumerate}

\section*{Notes for Future Batches}
\begin{itemize}
  \item If black currant’s tartness is too subtle in the beard, increase to 140 microliters; if too strong, reduce to 100 microliters.
  \item If violet leaf’s green crispness is not prominent, increase to 160 microliters; if overpowering, reduce to 120 microliters.
  \item If orange blossom’s floralcy dominates, reduce to 60 microliters; if too subtle, increase to 100 microliters.
  \item If lemon’s citrus sparkle is too faint, increase to 60 microliters; if too intense, reduce to 40 microliters.
  \item If frankincense’s resinous depth feels too heavy, reduce to 15 microliters; if too subtle, increase to 25 microliters.
  \item Warm viscous absolutes (black currant, violet leaf, boronia, orange blossom) to 40-50°C for easier handling.
  \item Store black currant absolute (~1.9g remaining) in the fridge; store orange blossom, neroli, pink pepper, coriander, lemon, frankincense in a cool, dark place.
  \item If DPG is unavailable, IPM is a suitable fallback, but ensure thorough mixing for absolutes.
  \item Test balm on skin for irritation, keeping oils/absolutes at approximately 1.04\% to minimize risk.
\end{itemize}

\vspace{1cm}
\begin{center}
\textcolor{violetPurple}{\rule{0.8\textwidth}{0.4pt}}
\end{center}

\begin{center}
\textit{\textcolor{colaDark}{A crisp, refreshing beard balm with tart fruity-floral notes, green crispness, and subtle resinous depth, crafted for a rugged yet refined storyteller.}}
\end{center}

\end{document}