\documentclass{article}
\usepackage{geometry}
\usepackage{xcolor}
\usepackage{titlesec}
\usepackage{enumitem}
\usepackage{fancyhdr}
\usepackage{booktabs}
\usepackage{array}

% Define cola-inspired colors
\definecolor{colaRed}{RGB}{201, 37, 44}     % Deep red like Coca-Cola logo
\definecolor{colaBrown}{RGB}{58, 29, 20}    % Dark brown like cola liquid
\definecolor{colaCream}{RGB}{253, 246, 227} % Light cream background
\definecolor{colaDark}{RGB}{45, 12, 7}      % Deep dark brown
\definecolor{violetPurple}{RGB}{138, 93, 150} % Violet flower color

% Page setup
\geometry{margin=1in}

% Header and footer setup
\pagestyle{fancy}
\fancyhf{}
\renewcommand{\headrulewidth}{0.4pt}
\renewcommand{\footrulewidth}{0.4pt}
\fancyhead[C]{\textcolor{violetPurple}{\textbf{Purple Balm}}}
\fancyfoot[C]{\textcolor{colaBrown}{\thepage}}

% Title format
\titleformat{\section}
  {\normalfont\Large\bfseries\color{colaRed}}
  {\thesection}{1em}{}

% Document begins
\begin{document}

\begin{center}
\textcolor{violetPurple}{\LARGE\textbf{Purple Balm}}\\[0.5cm]
\textcolor{colaBrown}{\large\textit{A natural, refreshing beard balm with a dry, periwinkle-like violet note, tart fruity-floral accents, citrus crispness, and subtle resinous depth}}\\[0.5cm]
\end{center}

\section*{Naturals-Only 30ml Beard Balm Recipe}

\begin{center}
\begin{tabular}{p{6.5cm}r}
\toprule
\textcolor{colaRed}{\textbf{Ingredient}} & \textcolor{colaRed}{\textbf{Amount}} \\
\midrule
\multicolumn{2}{l}{\textcolor{violetPurple}{\textbf{Base Composition:}}} \\
\midrule
Carnauba Wax & 4.5 grams (15\%) \\
Kokum Butter & 9 grams (30\%) \\
Squalane & 15.7 grams (52.33\%) \\
Scent Blend (Oils/Absolutes + Diluent) & 0.8 ml (2.67\%) \\
\midrule
\multicolumn{2}{l}{\textcolor{violetPurple}{\textbf{Scent Blend Composition (800 microliters):}}} \\
\midrule
3\% Deer Musk Tincture & 30 microliters \\
10\% Black Currant Bud Absolute (in IPM) & 80 microliters \\
10\% Violet Leaf Absolute (in IPM) & 200 microliters \\
10\% Boronia Absolute (in IPM) & 50 microliters \\
Orange Blossom Absolute & 50 microliters \\
Neroli EO & 5 microliters \\
Pink Pepper EO (undiluted) & 15 microliters \\
Coriander EO & 30 microliters \\
Lemon EO & 50 microliters \\
Lime EO & 20 microliters \\
10\% Frankincense Sacra DPG Dilution (Royal Green Hojari Omani) & 200 microliters \\
Dipropylene Glycol (DPG) or Isopropyl Myristate (IPM) & 300 microliters \\
\bottomrule
\end{tabular}
\end{center}

\vspace{0.5cm}

\section*{Concentration Analysis}
\begin{itemize}[leftmargin=*]
  \item \textcolor{colaRed}{\textbf{Floral-Fruity Notes (0.337\% in balm):}}
  \begin{itemize}
    \item 10\% Black Currant Bud Absolute: 80 microliters (0.027\% final)
    \item 10\% Violet Leaf Absolute: 200 microliters (0.067\% final)
    \item 10\% Boronia Absolute: 50 microliters (0.017\% final)
    \item Orange Blossom Absolute: 50 microliters (0.167\% final)
  \end{itemize}
  
  \item \textcolor{colaRed}{\textbf{Floral Support (0.017\% in balm):}}
  \begin{itemize}
    \item Neroli Essential Oil: 5 microliters (0.017\% final)
  \end{itemize}
  
  \item \textcolor{colaRed}{\textbf{Spice Notes (0.183\% in balm):}}
  \begin{itemize}
    \item Pink Pepper Essential Oil: 15 microliters (0.05\% final)
    \item Coriander Essential Oil: 30 microliters (0.1\% final)
  \end{itemize}
  
  \item \textcolor{violetPurple}{\textbf{Citrus Notes (0.234\% in balm):}}
  \begin{itemize}
    \item Lemon Essential Oil: 50 microliters (0.167\% final)
    \item Lime Essential Oil: 20 microliters (0.067\% final)
  \end{itemize}
  
  \item \textcolor{violetPurple}{\textbf{Resinous-Musk Notes (0.07\% in balm):}}
  \begin{itemize}
    \item 10\% Frankincense Sacra DPG Dilution: 200 microliters (0.067\% final, equivalent to 20 microliters pure EO)
    \item 3\% Deer Musk Tincture: 30 microliters (0.003\% final)
  \end{itemize}
  
  \item \textcolor{colaBrown}{\textbf{Carrier (Diluent in Scent Blend):}}
  \begin{itemize}
    \item Dipropylene Glycol (DPG) or Isopropyl Myristate (IPM): 300 microliters
  \end{itemize}
\end{itemize}

\section*{Expected Scent Profile}

\paragraph{\textcolor{colaRed}{\textbf{On Application:}}}
A striking burst of violet leaf’s dry, green, powdery floralcy, evoking a cool matte periwinkle shade, melds with black currant’s tangy fruitiness, lemon’s tart sparkle, and lime’s zesty, green lift. Pink pepper’s subtle fruity-spicy zing adds vibrancy, painting a sunlit Kyushu tea field with a crisp, floral breeze, humble yet bold.

\paragraph{\textcolor{colaBrown}{\textbf{Mid Wear (30 min - 2 hours):}}}
Violet leaf’s periwinkle-like floralcy shines, supported by boronia’s faint tea-like floralcy and orange blossom’s understated radiance. Coriander’s citrusy-spicy spark and neroli’s minimal honeyed glow add Rush-like freshness, while black currant’s tartness lingers, creating a tea field alive with dry violet blooms, its complexity slyly veiled by simplicity.

\paragraph{\textcolor{colaDark}{\textbf{Dry Down (2-6+ hours):}}}
Frankincense sacra’s subtle, balsamic warmth and deer musk’s musky depth emerge, grounding violet leaf’s powdery dryness with traces of boronia. The finish is understated, like a Scottish meadow at dusk, yet evocative, anchoring the periwinkle shade with a dry, chypre-like elegance.

\paragraph{\textcolor{violetPurple}{\textbf{Overall Performance:}}}
Purple Balm wears for 4-6 hours with subtle projection, a natural, artisanal blend centered on a dry, periwinkle-like violet note, with tart black currant, floral accents, zesty lemon-lime, and subtle resinous depth. It contrasts Peach Tea’s spicy chypre with summery, floral-green vibrancy, perfect for a half-Japanese, half-Scottish teacher’s rugged, bearded charm.

\section*{Preparation Instructions}
\begin{enumerate}
  \item \textbf{Pre-Blend Scent Compounds:}
  \begin{itemize}
    \item In a 1-2ml glass vial, combine the following in order, using separate micropipette tips:
    \begin{itemize}
      \item 3\% Deer Musk Tincture: 30 microliters
      \item 10\% Black Currant Bud Absolute (in IPM): 80 microliters
      \item 10\% Violet Leaf Absolute (in IPM): 200 microliters
      \item 10\% Boronia Absolute (in IPM): 50 microliters
      \item Orange Blossom Absolute: 50 microliters
      \item Neroli Essential Oil: 5 microliters
      \item Pink Pepper Essential Oil: 15 microliters
      \item Coriander Essential Oil: 30 microliters
      \item Lemon Essential Oil: 50 microliters
      \item Lime Essential Oil: 20 microliters
      \item 10\% Frankincense Sacra DPG Dilution: 200 microliters
    \end{itemize}
    \item Add 300 microliters of Dipropylene Glycol (DPG, preferred) or Isopropyl Myristate (IPM, fallback).
    \item Seal vial and roll gently for 1-2 minutes to blend, warming to 40-50°C if absolutes (black currant, violet leaf, boronia, orange blossom) are viscous.
    \item Rest for 1-2 hours (or up to 24 hours for optimal melding).
    \item Test on wrist, noting violet leaf’s dry, periwinkle-like floralcy, black currant’s tartness, lemon-lime’s citrus crispness, and frankincense sacra’s balsamic depth. Adjust if needed (e.g., add 10 microliters violet leaf for intensity).
  \end{itemize}
  \item \textbf{Melt Base:} In a double boiler, melt carnauba wax (4.5 grams) and kokum butter (9 grams) over low heat until liquid, stirring gently.
  \item \textbf{Add Squalane:} Remove from heat, add squalane (15.7 grams), and stir until blended.
  \item \textbf{Cool Slightly:} Cool to approximately 40-50°C to preserve the scent blend.
  \item \textbf{Add Scent Blend:} Add the pre-blended scent mixture (800 microliters) to the base, stirring gently to integrate.
  \item \textbf{Pour and Set:} Pour into a 30ml tin or jar while warm, cool at room temperature for 4-6 hours until solid, and seal tightly.
  \item \textbf{Test Application:} Apply a small amount to your beard, noting the prominence of violet leaf’s dry, periwinkle-like note, balanced by tartness, floral accents, citrus crispness, and resinous depth. Adjust in future batches if needed.
\end{enumerate}

\section*{Notes for Future Batches}
\begin{itemize}
  \item If violet leaf’s dry floralcy is too subtle, increase to 220 microliters; if overpowering, reduce to 180 microliters.
  \item If black currant’s tartness fades in the beard, increase to 100 microliters; if too strong, reduce to 60 microliters.
  \item If orange blossom or neroli contributes to soapiness, reduce orange blossom to 40 microliters or neroli to 0 microliters.
  \item If lemon-lime’s citrus crispness is too faint, increase lemon to 60 microliters or lime to 30 microliters; if too intense, reduce lemon to 40 microliters and lime to 10 microliters.
  \item If frankincense sacra’s balsamic depth feels too heavy, reduce to 150 microliters; if too subtle, increase to 250 microliters.
  \item Warm viscous absolutes (black currant, violet leaf, boronia, orange blossom) to 40-50°C for easier handling.
  \item Store black currant absolute (~1.9g remaining) in the fridge; store orange blossom, neroli, pink pepper, coriander, lemon, lime, frankincense sacra in a cool, dark place.
  \item If DPG is unavailable, IPM is a suitable fallback, but ensure thorough mixing for absolutes.
  \item Test balm on skin for irritation, keeping oils/absolutes at approximately 1.04\% to minimize risk.
  \item When osmanthus absolute arrives, consider adding 20 microliters to enhance peachy radiance, reducing black currant to 60 microliters.
  \item When juniper berry CO2 arrives, consider adding 20 microliters for coniferous crispness, reducing pink pepper to 10 microliters.
\end{itemize}

\vspace{1cm}
\begin{center}
\textcolor{violetPurple}{\rule{0.8\textwidth}{0.4pt}}
\end{center}

\begin{center}
\textit{\textcolor{colaDark}{A crisp, refreshing beard balm with a dry, periwinkle-like violet note, tart fruity-floral accents, zesty citrus, and subtle balsamic depth, crafted for a rugged yet refined storyteller.}}
\end{center}

\end{document}