\documentclass{article}
\usepackage{geometry}
\usepackage{xcolor}
\usepackage{titlesec}
\usepackage{enumitem}
\usepackage{fancyhdr}
\usepackage{booktabs}
\usepackage{array}

% Defining colors
\definecolor{colaRed}{RGB}{201, 37, 44}     % Deep red for emphasis
\definecolor{colaBrown}{RGB}{58, 29, 20}    % Dark brown for text
\definecolor{colaCream}{RGB}{253, 246, 227} % Light cream background
\definecolor{colaDark}{RGB}{45, 12, 7}      % Deep dark brown
\definecolor{violetPurple}{RGB}{138, 93, 150} % Violet flower color

% Setting page geometry
\geometry{margin=1in}

% Configuring header and footer
\pagestyle{fancy}
\fancyhf{}
\renewcommand{\headrulewidth}{0.4pt}
\renewcommand{\footrulewidth}{0.4pt}
\fancyhead[C]{\textcolor{violetPurple}{\textbf{Peach Tea Fragrance}}}
\fancyfoot[C]{\textcolor{colaBrown}{\thepage}}

% Formatting section titles
\titleformat{\section}
  {\normalfont\Large\bfseries\color{colaRed}}
  {\thesection}{1em}{}

% Beginning document
\begin{document}

\begin{center}
\textcolor{violetPurple}{\LARGE\textbf{Peach Tea}}\\[0.5cm]
\textcolor{colaBrown}{\large\textit{A natural tea field with floral-tea warmth, meadow citrus, and bright resinous depth}}\\[0.5cm]
\end{center}

\section*{Naturals-Only 1ml Fragrance Recipe}

\begin{center}
\begin{tabular}{p{6.5cm}r}
\toprule
\textcolor{colaRed}{\textbf{Ingredient}} & \textcolor{colaRed}{\textbf{Amount}} \\
\midrule
\multicolumn{2}{l}{\textcolor{violetPurple}{\textbf{Order of Addition (Bottom to Top):}}} \\
\midrule
IPM (Carrier) & 754 microliters \\
3\% Deer Musk Tincture & 20 microliters \\
10\% Boronia Absolute (in IPM) & 15 microliters \\
10\% Black Currant Bud Absolute (in IPM) & 8 microliters \\
10\% Violet Leaf Absolute (in IPM) & 10 microliters \\
10\% Royal Green Hojari Frankincense Tincture (in IPM) & 15 microliters \\
Neroli EO & 18 microliters \\
Pink Pepper EO (undiluted) & 10 microliters \\
Ceylon Cinnamon EO & 5 microliters \\
Lime EO & 20 microliters \\
Lemon EO & 20 microliters \\
Bergamot EO & 33 microliters \\
\bottomrule
\end{tabular}
</center>

\vspace{0.5cm}

\section*{Concentration Analysis}
\begin{itemize}[leftmargin=*]
  \item \textcolor{colaRed}{\textbf{Citrus Notes (7.3\%):}}
  \begin{itemize}
    \item Bergamot EO: 33 microliters (3.3\%)
    \item Lemon EO: 20 microliters (2\%)
    \item Lime EO: 20 microliters (2\%)
  \end{itemize}
  
  \item \textcolor{colaRed}{\textbf{Spice Elements (1.5\%):}}
  \begin{itemize}
    \item Ceylon Cinnamon EO: 5 microliters (0.5\%)
    \item Pink Pepper EO: 10 microliters (1\%)
  \end{itemize}
  
  \item \textcolor{violetPurple}{\textbf{Floral-Tea-Fruity-Resin Notes (3.2\%):}}
  \begin{itemize}
    \item 10\% Boronia Absolute: 15 microliters (0.15\% final)
    \item 10\% Black Currant Bud Absolute: 8 microliters (0.08\% final)
    \item 10\% Violet Leaf Absolute: 10 microliters (0.1\% final)
    \item 10\% Royal Green Hojari Frankincense Tincture: 15 microliters (0.15\% final)
    \item Neroli EO: 18 microliters (1.8\%)
    \item 3\% Deer Musk Tincture: 20 microliters (0.06\% final)
  \end{itemize}
  
  \item \textcolor{colaBrown}{\textbf{Carrier:}}
  \begin{itemize}
    \item Isopropyl Myristate (IPM): 754 microliters (75.4\%)
  \end{itemize}
\end{itemize}

\section*{Expected Scent Profile}

\paragraph{\textcolor{colaRed}{\textbf{Top Notes (5-30 minutes):}}}
**Peach Tea** opens with a crisp, unassuming burst of **bergamot**, **lemon**, and **lime**, their citrus zest painting a sunlit meadow with a fresh, inviting glow. **Pink pepper**’s fruity-spicy spark dances alongside **violet leaf**’s delicate purple-green fizz, evoking a dawn tea field that’s simple yet subtly vibrant, like your quiet entry into a Massachusetts classroom, hinting at the depth beneath.

\paragraph{\textcolor{colaBrown}{\textbf{Heart Notes (30 min - 3 hours):}}}
The heart blooms with **boronia**’s pu-erh tea-like floralcy, a gentle, tea-steeped warmth that intertwines with **neroli**’s radiant, honeyed embrace. A whisper of **black currant**’s tangy fruitiness adds a fleeting, delicate lift, while **ceylon cinnamon**’s soft, spicy glow weaves in a trace of Scottish fire. This tea field is understated, like your measured wisdom as a teacher, but slyly complex, its floral-tea notes lingering like memories of Kyushu’s serene orchards, with a nod to Gucci Rush’s vibrant heart.

\paragraph{\textcolor{colaDark}{\textbf{Base Notes (3-6+ hours):}}}
The base settles into **Royal Green Hojari frankincense**’s bright, resinous warmth, its citrusy-resinous depth glowing like embers in a tea shop, carrying a whisper of sacred ritual. **Deer musk**’s gentle, musky sweetness anchors the scent, offering a soft, resinous elegance that’s humble, like a worn leather journal, yet misleadingly profound, evoking a New England forest at dusk or a Scottish moor’s quiet strength, grounding your rugged, storytelling soul.

\paragraph{\textcolor{violetPurple}{\textbf{Overall Impression:}}}
**Peach Tea** is a natural, artisanal fragrance that wears for 4-6 hours with moderate projection, embodying a humble, understated simplicity that belies its rich depth. Its floral-tea heart, meadow-citrus sparkle, and bright resinous base capture your half-Japanese, half-Scottish essence—a rugged storyteller blending Kyushu’s tea fields with Scottish warmth. Inspired by Gucci Rush’s chypre elegance, this spare interpretation leans floral-resinous, offering a quiet, authentic signature for your classroom lessons or New England trails, with a simplicity that’s slyly complex, true to your understated yet profound persona.

\section*{Preparation Instructions}
\begin{enumerate}
  \item Prepare 1 ml of 10\% Royal Green Hojari frankincense tincture by mixing 200 microliters of 50\% frankincense tincture (in DPG) with 800 microliters of IPM; shake well to ensure homogeneity.
  \item Begin with IPM carrier in a 1ml vial.
  \item Add each ingredient in the specified order, using separate micropipette tips for each.
  \item Warm viscous absolutes (e.g., boronia, black currant, violet leaf) to 40-50°C for easier handling.
  \item Seal vial and roll gently to blend without introducing air bubbles.
  \item Allow to rest 24-48 hours in a cool, dark place for notes to meld.
  \item Test on skin or beard, noting the balance of boronia’s tea-like floralcy and frankincense’s resinous depth; adjust black currant (6-10 microliters) or frankincense tincture (10-20 microliters) if needed, mindful of limited supply (1 ml after dilution).
\end{enumerate}

\section*{Notes for Future Batches}
\begin{itemize}
  \item If black currant feels too tangy, reduce to 6 microliters; if fruitiness is weak, increase to 10 microliters (per original LaTeX notes).
  \item If frankincense is too prominent, reduce to 10 microliters; if resinous depth is weak, increase to 20 microliters (conserve 1 ml supply).
  \item Consider remaking 10\% dilutions in DPG for smoother blending (per original LaTeX notes).
  \item Store black currant absolute (~1.9g remaining) in the fridge; keep frankincense tincture and other EOs/absolutes in a cool, dark place.
  \item Warm viscous ingredients to 40-50°C for 10-15 minutes to improve handling (per original LaTeX notes).
\end{itemize}

\end{document}